\blue{...Numerical investigation of viscous flow instabilities through heterogeneous porous media using adaptive and unstructured meshes under different mobility scenarios...}

### 2017-07-11 Papers/ViscousInstabilities/article_figure1.tex
update

%%%%
%%%%  FIGURE
%%%%
\begin{landscape}
\begin{figure}[ht] 
\vbox{
\hbox{\hspace{4.0cm}
\includegraphics[width=.75\textwidth]{./Pics/map_of_boundaries.pdf} 
}
\vspace{0.0cm}
\hbox{\hspace{6.5cm} (a) Schematics of the domain
}
\vspace{0.25cm}
\hbox{\hspace{4.0cm}
\includegraphics[width=.9\textwidth]{./Pics/map_of_boundaries_1.pdf}
}
\vspace{0.0cm}
\hbox{\hspace{9cm} (b)      
}
}     
\caption{Impact of mesh resolution on flow instabilities: (a) schematics of the domain depicting four regions with prescribed synthetic permeabilities; (b) there is a comparison between the unstructured and fixed mesh and the unstructured and adaptive mesh. During the implementation of fixed mesh initially there $4606$ elements while for the adaptive mesh there are $606$ while the majority of them is on the interface between between the two fluids. }
\label{fig:testcase_heter_domain}
\end{figure}
\end{landscape}
\clearpage

>>>>

%%%%
%%%%  FIGURE
%%%%
\begin{landscape}
\begin{figure}[ht] 
\vbox{
\hbox{\hspace{4.0cm}
\includegraphics[width=.75\textwidth]{./Pics/map_of_boundaries.pdf} 
}
\vspace{0.0cm}
\hbox{\hspace{6.5cm} (a) Schematics of the domain
}
\vspace{0.25cm}
\hbox{\hspace{4.0cm}
\includegraphics[width=.9\textwidth]{./Pics/Four_regions_coarse_MeshPermeability}
}
\vspace{0.0cm}
\hbox{\hspace{9cm} (b)      
}
}     
\caption{Impact of mesh resolution on flow instabilities: (a) schematics of the simulated domain; (b) permeability distribution with grid resolution in the simulation performed with a coarse mesh (there are 1292 \PN[1]{2} element-pairs in the domain).}
\label{fig:testcase_heter_domain}
\end{figure}
\end{landscape}
\clearpage
